Reading Notes

### 2020-07-09 paper.tex
reading some mosdef references

>>>>

\cite{Cummings2019}
each research group used to maintain their own code ,but now these codes are general purpose and shared. open source aid reproducibility because (1) users can look at the source code to find bug and these can be very quickly fixed, (2) monetary cost can exclude users who can't afford it.
a disadvantage is that open source software may be less new user friendly and instead of a gui may use scripts. scripts are an advantage to reproducability however because they allow for user to show and version control exactly what they did with little to no ambiguity. GUI's may obscure the actual mehtod.
ooh I want to look at etomica. hmm. doesnt work in my browser.
overall this was a good summary of what exists but no big takeaways
